{\small} High Performance P$^{3}$M N-body code: CUBEP3M

### 2012-07-31 paper_new.tex
Improved the text about the kernel correction

%\begin{figure}%[ht]
 % \begin{center}
  %   \includegraphics[width=3.2in]{graphs/densityForce_ppext=10_rebin.eps}
  %\caption{ Gravity force in of the P$^3$M algorithm, versus distance in fine mesh cell units, compared with the exact $1/r^{2}$ law.
   % This particular calculation was obtained in a CITA128 realization with  a box size of $100 h^{-1}\mbox{Mpc}$, averaged over 10 time steps.
   % Results are rebined to show how well the mean value follows the thoretical curve down to the grid size.
   % \label{fig:F_rebin}}
%\end{center}
%\end{figure}
Although most of the code tests presented in this paper were obtained with the configuration described above, 
we present here a recent improvement in the fine force kernel that compensates for the systematic underestimate
at grid distances. Basically, the idea is to boost the small distance elements of the kernel by a small amount,
which somehow corrects for the loss observed in the bottom panels of Fig. \ref{fig:den_force_fracErr}.
We show here the impact of three different trials: a) the force from the first layer of neighbours is boosted by $90$ per cent, b)
the force from the first two layers of neighbours is boosted by $60$ per cent, and c) by $80$ per cent.
We observe that we are able to improve the power at turn around by almost a factor of two, which doubles the resolution.  
This test was performed in a series of SciNet256 simulations with a volume of $150 h^{-1} \mbox{Mpc}$ and at $z=0$.
We see from the figure that in the original configuration, the departure from the non-linear predictions occur at $k\sim 3.0 h\mbox{Mpc}^{-1}$,
whereas the third trial allows for a resolution down to $k\sim 6.0 h\mbox{Mpc}^{-1}$. 
%We note that these trials have not yet been 
%tried on very large runs, and we recommend that some more testing should be done to assess the robustness of this correction.

>>>>

%\begin{figure}%[ht]
 % \begin{center}
  %   \includegraphics[width=3.2in]{graphs/densityForce_ppext=10_rebin.eps}
  %\caption{ Gravity force in of the P$^3$M algorithm, versus distance in fine mesh cell units, compared with the exact $1/r^{2}$ law.
   % This particular calculation was obtained in a CITA128 realization with  a box size of $100 h^{-1}\mbox{Mpc}$, averaged over 10 time steps.
   % Results are rebined to show how well the mean value follows the thoretical curve down to the grid size.
   % \label{fig:F_rebin}}
%\end{center}
%\end{figure}
Although most of the code tests presented in this paper were obtained with the configuration described above, 
we present here a recent improvement in the fine force kernel that compensates for the systematic underestimate
at grid distances. Basically, the idea is to boost the small distance elements of the kernel by a small amount,
which somehow corrects for the loss observed in the bottom panels of Fig. \ref{fig:den_force_fracErr}.
We show here the impact of three different trials: a) the force from the first layer of neighbours is boosted by $90$ per cent, b)
the force from the first two layers of neighbours is boosted by $60$ per cent, and c) by $80$ per cent.
We observe that with the trial a), we are able to improve the power at turn around by a factor of $1.5$, which almost doubles the resolution.  
This test was performed in a series of SciNet256 simulations with a volume of $150 h^{-1} \mbox{Mpc}$ and at $z=0$.
We see from the figure that in the original configuration, the departure from the non-linear predictions occur at $k\sim 3.0 h\mbox{Mpc}^{-1}$,
whereas the first trial allows for a similar resolution down to $k\sim 4.5 h\mbox{Mpc}^{-1}$. 
Other correction schemes are more aggressive, and although they recover power at even smaller scales, 
they exhibit a small overestimate compare to non-linear predictions in the range $2.0 < k < 4.0 h\mbox{Mpc}^{-1}$, 
and more testing should be done prior to using these corrections.

We therefore recommend that the fine force kernel should be considered as an adjustable parameter;
`no correction' is considered as the  conservative mode, which is accurate only up to the resolution turn around 
observed in the dimensionless power spectrum. Higher resolution can be achieved with the modified fine force kernel following `trial a',
and should be considered as an actual resolution improvement, with no cost in accuracy nor in run time;
`trial b' and `trial c' should be considered as too aggressive. We note that we have not exhausted the list of possible correction,
and that future work in that direction might result in even better resolution.

%We note that these trials have not yet been 
%tried on very large runs, and we recommend that some more testing should be done to assess the robustness of this correction.
